Case study validations of automatic bullet matching

### 2018-10-26 index.Rmd
comment

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
 && \multicolumn{3}{l}{\bf AUC (95\% Conf. Int)}\\
\bf Study & \bf Set & \bf RF score & \bf Cross-correlation & \bf CMS \\
  \hline
\bf Hamby 44 &  & 0.937 (0.917, 0.957) & 0.916 (0.891, 0.941) & 0.820 (0.787, 0.854) \\
\bf  Phoenix PD &  & 0.976 (0.957, 0.994) & 0.986 (0.975, 0.996) & 0.879 (0.838, 0.919) \\
\bf  Houston FSI & Set 1 & 0.991 (0.983, 0.999) & 0.988 (0.979, 0.997) & 0.785 (0.727, 0.842) \\
\bf  Houston FSI & Set 2 & 0.898 (0.853, 0.943) & 0.902 (0.861, 0.943) & 0.749 (0.684, 0.814) \\
\bf  Houston FSI & Set 3 & 0.986 (0.973, 0.999) & 0.987 (0.978, 0.997) & 0.911 (0.880, 0.941) \\
   \hline
\end{tabular}
\caption{Area under the curve (AUC) for each (set) of the studies for the random forest score, cross-correlation and CMS. Overall the perform on all sets is very good to excellent for cross-correlation and the random forest score.  As seen in the ROC curves, the algorithm performs the least well on set 2 of the Houston FSI study.  At the land level there is no significant difference in prediction power between RF score and cross-correlation.} \label{tab:aucs}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
 && \multicolumn{3}{l}{\bf AUC (95\% Conf. Int)}\\
\bf Study & \bf Set & \bf RF score & \bf Cross-correlation & \bf CMS \\
  \hline
\bf Hamby 44 &  & 0.937 (0.917, 0.957) & 0.916 (0.891, 0.941) & 0.820 (0.787, 0.854) \\
\bf  Phoenix PD &  & 0.976 (0.957, 0.994) & 0.986 (0.975, 0.996) & 0.879 (0.838, 0.919) \\
\bf  Houston FSI & Set 1 & 0.991 (0.983, 0.999) & 0.988 (0.979, 0.997) & 0.785 (0.727, 0.842) \\
\bf  Houston FSI & Set 2 & 0.898 (0.853, 0.943) & 0.902 (0.861, 0.943) & 0.749 (0.684, 0.814) \\
\bf  Houston FSI & Set 3 & 0.986 (0.973, 0.999) & 0.987 (0.978, 0.997) & 0.911 (0.880, 0.941) \\
   \hline
\end{tabular}
\caption{\svp{Can we turn this into a picture? It's really dense and hard to interpret...}Area under the curve (AUC) for each (set) of the studies for the random forest score, cross-correlation and CMS. Overall the perform on all sets is very good to excellent for cross-correlation and the random forest score.  As seen in the ROC curves, the algorithm performs the least well on set 2 of the Houston FSI study.  At the land level there is no significant difference in prediction power between RF score and cross-correlation.} \label{tab:aucs}
\end{table}
